---
title: "Fraud Detection"
author: "Ivan Liu"
date: "Friday, August 22, 2014"
output: html_document
---
<br/>
#### Data explorasion
```{r, echo=FALSE, message=F, tidy=TRUE,comment=NA}
require(DMwR)
data(sales)
head(sales, n=5)
```
ID - a factor with the ID of the salesman.<br/>
Prod - a factor indicating the ID of the sold product.<br/>
Quant - the number of reported sold units of the product.<br/>
Val - the reported total monetary value of the sale.<br/>
Insp - a factor with three possible values: ok if the transaction was
inspected and considered valid by the company, fraud if the transaction
was found to be fraudulent, and unkn if the transaction was not inspected
at all by the company.<br/>

```{r, echo=FALSE, message=F, tidy=TRUE,comment=NA}
summary(sales)
nlevels(sales$ID)
nlevels(sales$Prod)
sum(is.na(sales$Quant)& is.na(sales$Val))
table(sales$Insp)/nrow(sales)*100
```

```{r, echo=FALSE, message=F, tidy=TRUE,comment=NA, fig.width=10}
totS <- table(sales$ID)
totP <- table(sales$Prod)
par(mfcol = c(1,2))
barplot(totS, main="Transactions per salespeople", names.arg='',
        xlab='Salespeople',ylab='Amount')
barplot(totP, main='Transactions per product', names.arg='',
        xlab='Products',ylab='Amount')
```